### 2022-12-08 README.Rmd
add instructions for installing from the r universe

to install the package.

>>>>

to install the package. Alternatively, binary packages of the development
version are available from rOpenSci's R Universe service:

```{r install-r-universe, eval = FALSE}
# Enable repository from gavinsimpson
options(repos = c(
  gavinsimpson = "https://gavinsimpson.r-universe.dev",
  CRAN = "https://cloud.r-project.org"))

# Download and install gratia in R
install.packages("gratia")
```
